---
title: "Lab 1 - Data visualization"
author: "Sydney Girvin"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)

library(viridis)
```

## Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

```{r ex-1}
ggplot(data = midwest, mapping = aes(x = popdensity)) +
  geom_histogram(binwidth = 10000)
```

The data is greatly skewed to the right. There appears to be outliers between 50000 and 75000 as well as after 75000.

## Exercise 2

```{r ex-2}
ggplot(data = midwest, mapping = aes(x = percollege, y = percbelowpoverty, color = state)) +  
     geom_point() +
        scale_color_viridis_d()
```

## Exercise 3

There is a large clump of states around 10-25% of people with a collge degree and below poverty. There is a substanial outlier from the state of Wyoming. This outlier falls in the 0-10% of people with a college degree but also in the 50% of people living below poverty. ???

## Exercise 4

```{r ex-4}
ggplot(data = midwest, mapping = aes(x = percollege, y = percbelowpoverty, color = state)) +  
     geom_smooth(se = FALSE) 
```

Which plot do you prefer - this plot or the plot in Ex 2? Briefly explain your choice.

I prefer this plot because it is easier to read.

## Exercise 5



## Exercise 6

## Exercise 7
