---
title: "Lab 1 - Data visualization"
author: "Sydney Girvin"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)

library(viridis)
```

## Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

```{r ex-1}
ggplot(data = midwest, mapping = aes(x = popdensity)) +
  geom_histogram(binwidth = 10000)
```

The data is greatly skewed to the right. There appears to be outliers between 50000 and 75000 as well as after 75000.

## Exercise 2

```{r ex-2}
ggplot(data = midwest, mapping = aes(x = percollege, y = percbelowpoverty, color = state)) +  
     geom_point() +
        scale_color_viridis_d()
```

## Exercise 3

There is a large clump of states in this graph making it hard to interpret. It seems that Ohio has a large amount of people living below the poverty line and not a lot of people with college degrees. For Illinois, it seems like more people have college degrees due to the purple dots off to the right side of the graph.

## Exercise 4

```{r ex-4}
ggplot(data = midwest, mapping = aes(x = percollege, y = percbelowpoverty, color = state)) +  
     geom_smooth(se = FALSE) +
  labs(x = "% of people with college degree", 
       y = "% of people living below poverty",
       title = "Relationship Between College Degrees and Poverty by State",
       color = "State")
```

I prefer this plot from exercise 4 because it is easier to read. It is easier to see the trends here by dragging a finger and mapping what is on the X axis to what is on the Y axis.

## Exercise 5

```{r ex-5}
ggplot(data = midwest, mapping = aes(x = area,color = state)) + 
  geom_boxplot()
```

Wisconsin's median is larger than the other states. The red and purple one have the most variability, they are the most spread out.

-   Which state has the single largest county? How do you know based on the plot?

## Exercise 6

```{r ex-6}
midwest <- midwest |>
  mutate(metro = if_else(inmetro == 1, "Yes", "No"))
     ggplot(midwest, 
       aes(x = state, fill = metro)) +
           geom_bar(position = "fill") +
           labs(title = "state vs percentage in metro area", x = "State", y = "Percentage in metro area")
```

## Exercise 7

```{r ex-7}
ggplot(midwest, aes(x= percollege, y = popdensity, color= percbelowpoverty)) + 
  geom_point(alpha = .5) +
  facet_wrap(~state) +
  labs(title = "College Degree vs Population Density", x = "% College Educated" , y = "Population Density", color = "% Below Poverty Line") + 
  theme_minimal()
```
